Supersymmetric Dirac-Born-Infeld Axionic Inflation and Non-Gaussianity

### 2018-09-17 SUSY_DBI.tex
Arxiv version

\documentclass[a4paper,11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\non{\nonumber\\}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jheppub} % for details on the use of the package, please
                     % see the JHEP-author-manual

\usepackage[T1]{fontenc} % if needed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\rr}[1]{{\color{red}{#1}}}
\newcommand{\bl}[1]{{\color{blue}{#1}}}
\newcommand{\gr}[1]{{\color{green}{#1}}}
\newcommand{\brown}[1]{{\color{brown}{#1}}}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{green}{rgb}{0.2,0.5,0.2}
\newcommand{\maxdelete}[1]{{\color{orange}{#1}}}
\newcommand{\maxadd}[1]{{\color{green}{#1}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{hyperref}
%%%%
\usepackage{cleveref}
\crefname{equation}{Eq.}{Eqs.}
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
\crefname{section}{Section}{Sections}
\newcommand{\crefrangeconjunction}{--}
%%%%%%%%%%%%%%%%%%%%
\def\TeV{\rm{TeV}}

\def\co{coannihilation~}
\def\G{\tilde G}
\def\mP{M_\text{P}}

\def\non{\nonumber\\}
\def\a{{\cal a}}
\def\vp{\phi}
\def\k{ \sqrt{ \gamma + \delta \cos (\alpha a/2f)}}
\def\kk{ \gamma + \delta \cos (\alpha a/2f)}

\def\F{{\cal F}}

\title{\boldmath Supersymmetric Dirac-Born-Infeld Axionic Inflation and Non-Gaussianity}
\author{Pran Nath}
\author{and Maksim Piskunov}
\affiliation{Department of Physics, Northeastern University,\\Boston, MA 02115-5000, USA}
% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{p.nath@northeastern.edu}
\emailAdd{m.piskunov@northeastern.edu}

\abstract{
  An analysis is given of inflation based on a supersymmetric Dirac-Born-Infeld (DBI) action in
  an axionic landscape. The DBI model we discuss involves a landscape of chiral superfields with one
  $U(1)$ shift symmetry which is broken by instanton type non-perturbative terms
  in the superpotential. Breaking of the shift symmetry leads to one pseudo-Nambu-Goldstone-boson which acts as
  the inflaton while the remaining normalized phases of the chiral fields
  generically labeled axions are invariant under the
  $U(1)$ shift symmetry. The analysis is carried out in the vacuum with stabilized saxions,
 which are the magnitudes of
  the chiral fields. Regions of the parameter space where slow-roll inflation occurs are exhibited and the spectral
  indices as well as the ratio of the tensor to the scalar power spectrum are computed. An interesting aspect of supersymmetric
  DBI models analyzed is that in most of the parameter space tensor to scalar ratio and scalar spectral index are consistent with
   Planck data if     slow roll occurs and is not eternal. Also interesting is that
  the ratio of the tensor to the scalar power spectrum can be large and can lie close to the
  experimental upper limit and thus testable in improved
  experiment. Non-Gaussianity in this
  class of models is explored.
}

\begin{document} 
\maketitle
\flushbottom
\fbox{{\today}}

@@

    k=\beta \sqrt{\sum_{m, n}m n G_mG_n \left(1-\cos\left(\frac{a_- m}{\sqrt 2 f}\right)-\cos\left(\frac{a_- n}{\sqrt 2 f}\right)+\cos\left(\frac{a_- \left(m-n\right)}{\sqrt 2 f}\right)\right)},

@@

    G_k = \frac{A_k 2^{1/2 (1 - k)}}{\beta \sqrt T f^{1-k}}\,.

@@

  Here $\beta$ is an arbitrary dimensionless parameter which we choose such that $G_k \sim 1$, and which determines the scale of symmetry breaking terms relative to $T$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pressure, density and inflation equations \label{sec4}}
  The pressure $p$ and density $\rho$ are defined in terms of the stress tensor by
  \begin{equation}\label{DisplayFormulaNumbered:eq.pressure}
    p= \frac{1}{3} \sum_{i=1}^3 T^{ii}\,,
    ~~\rho =T^{00},
  \end{equation}
  where $T^{\mu\nu}$ $(\mu=0, 1, 2, 3)$ is the stress tensor and is given by
  \begin{equation}
    T^{\mu \nu}=g^{\mu \nu} \mathcal{L}\left(\phi_k,\partial_\mu \phi_k \partial^\mu \phi_k \right)-2\frac{\delta \mathcal{L}\left(\phi_k,\partial_\mu \phi_k \partial^\mu \phi_k \right)}{\delta \left(\partial_\mu \phi_k \partial^\mu \phi_k \right)}\partial^\mu \phi_k \partial^\nu \phi_k,
    \label{tmunu}
  \end{equation}
  and we use the metric $\eta^{\mu\nu}= {\rm diag}(-1, 1, 1, 1)$.
  In the analysis we assume space to be homogeneous and isotropic, so that $\partial_i\phi_k = 0$ for $1 \leq i \leq 3$ and 
	$\partial_0 \phi_{k} = \dot{\phi}_k$,
  one finds that Eqs. (\ref{DisplayFormulaNumbered:eq.pressure}) and (\ref{tmunu})
  for pressure and density become:
  \begin{equation}\label{DisplayFormulaNumbered:eq.pressure.cosmology}
    p = \mathcal{L}\left(\phi_k, - \beta_k \right),
  \end{equation}
  and
  \begin{equation}\label{DisplayFormulaNumbered:eq.density.cosmology}
    \rho = -\mathcal{L}\left(\phi_k, - \beta_k\right) + 2\sum_{k}\frac{\delta \mathcal{L}\left(\phi_k, - \beta_k \right)}{\delta \beta_k}
    \beta_k,
  \end{equation}
  where $\beta_k = \dot \phi_k^2$.
  These relations are valid for non-canonical kinetic terms.
  The Friedman equations are given by
  \begin{align}
    \dot \rho = -3H (p + \rho),
    \label{fried1}
  \end{align}
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = \rho,
    \label{fried2}
  \end{align}
  \begin{align}
    \dot\rho= - 6H \sum_{k} \frac{\partial L}{\partial \beta_k} \beta_k\,.
    \label{rhodot1}
  \end{align}
  Further taking the time derivative of Eq.~(\ref{DisplayFormulaNumbered:eq.density.cosmology})
  which along with Eq.~(\ref{rhodot1}) gives
  \begin{align}
    &\sum_{k}\Big[ \left(2 \frac{\partial^2 L}{\partial \beta_k \partial \beta_k} \beta_k + \frac{\partial L}{\partial \beta_k}
    \right)\dot \beta_k
    - \frac{\partial L}{\partial \phi_k} \dot \phi_k + 6H \frac{\partial L}{\partial \beta_k} \beta_k
    + 2 \frac{\partial^2 L}{\partial \phi_k\partial \beta_k} \beta\dot \phi_k \Big]=0.
    \label{motion}
  \end{align}
  Next we focus on the slow-roll part where we keep only the field $a_-$. In this case Eqs. (\ref{fried2}) and (\ref{motion}) can be written in
  the following form
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = 2 \dot a_{-}^2 \frac{\partial L}{\partial \dot a_{-}^2} - L\,,
    \label{inf-1a}
  \end{align}
  \begin{align}
    2 \left[2 \frac{\partial^2 L}{\partial \dot a_{-}^2 \partial \dot a_{-}^2} \dot a_{-}^2 + \frac{\partial L}{\partial \dot a_{-}^2}
    \right] \ddot a_{-} -
    \frac{\partial L}{\partial a_{-}} + 6H \dot a_{-} \frac{\partial L}{\partial \dot a_{-}^2}
    + 2 \frac{\partial^2 L}{\partial a_{-} \partial \dot a_{-}^2} \dot a_{-}^2
    =0
    \label{inf-2a}\,.
  \end{align}
  For the case of canonical kinetic energy and no dependence of the potential on time derivative of field, i.e.,
  \begin{align}
    L= -\frac{1}{2} \partial_\mu a_{-}\partial a_{-}^{\mu} - V(a_-)
  \end{align}
  the above equations reduce to the following
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = \frac{1}{2} \dot a_{-}^2 + V(a_-)\,,\non
    \ddot a_{-} + 3 H \dot a_{-} + V'(a_{-})=0\,,
  \end{align}
  which are correctly the relation for slow roll for the case when one has canonical kinetic energy and the potential
  is velocity independent. However, in our case we have more terms.

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig1.pdf}
    \caption{
      Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the scalar spectral index $n_s$
      for the two field DBI model when $\alpha_1$ is allowed to vary, when $\alpha_2 = \alpha_3 = 0$. The plot shows that $89\%$ of simulated points are consistent with Planck constraints as shown in blue. Right panel: A plot of non-Gaussianity parameter $f_{NL}$ as
      a function of $\alpha_1$ for the same data set as in the left plot. The green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region 
      and the red dots are parameter points which are outside the experimentally allowed region. Black line corresponds to the 
 lower limit $f_{NL} =5$ of the 
        projected value for observation in future experiments for non-Gaussianity.
           The points that lie above the black line give non-Gaussianity $f_\text{NL} > 5$ which, however, are not consistent with Eq.~(\ref{data}).
    }
    \label{fig1}
  \end{figure}

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig2.pdf}
    \caption{Left panel: A plot of the ratio $n_s$ vs $N_{\rm pivot}$ in the range $50-60$ for the same data set as in Fig.~(\ref{fig1}).
    The plot shows a mild dependence of $n_s$ on $N_{\rm pivot}$ in the range indicated. Right panel: The same as the left panel except
    $f_{NL}$ is plotted vs $N_{\rm pivot}$.
    The green and red dots are parameter points and have the same meaning as in Fig.~(\ref{fig1}).}
    \label{fig2}
  \end{figure}

  \begin{figure}
  	\centering
  	\includegraphics[width=1.0\textwidth]{figs/fig3.pdf}
  	\caption{The effect of $\alpha_2$ (left panel) and $\alpha_3$ (right panel) on non-Gaussianity for a parameter point 
	taken from Fig.~(\ref{fig1}) which is consistent with 
	Planck data and has the  largest non-Gaussianity among the set of parameter points 
  in Fig.~(\ref{fig1}). Specifically, here $f = 0.429 M_\text{P}$, $a_{-, 0} = 0.233 M_\text{P}$, $\dot a_{-, 0} = -0.118 M_\text{P}^2$, $G_1 = G_2 = G_3 = 0$, $G_4 = 1$, $G_5 = -1.53$, $G_6 = 563$, $\alpha_1 = 1207$, $\beta = 0.802$, $T = M_\text{P}^4$. One 
	finds that 
	 the effect is not sufficient to obtain a significantly larger value of $f_\text{NL}$.}
  	\label{fig3}
  \end{figure}

Numerical simulations performed consist of two parts: a large $0.5 \times 10^6$ points simulation in which $\alpha_2 = \alpha_3 = 0$, and a small simulation with $\alpha_2$ and $\alpha_3$ perturbed around an experimentally consistent point with the largest non-Gaussianity from the first simulation.

  The evolution of the inflaton field $a_-$ in the large simulation Figs.~(\ref{fig1}) and (\ref{fig2}) is obtained by taking the effective axion Lagrangian Eqs.~(\ref{eq.axionLagrangian.I}) and (\ref{eq.axionLagrangian.II}), deriving Euler-Lagrange equation and Friedmann Eq.~(\ref{fried2}) using computer algebra, and solving them numerically. The integration is stopped when the ratio of the time derivative ($\dot n\left(t\right)$) of the e-foldings count to its time-average ($n\left(t\right) / t$) passes a threshold. Specifically,
  \begin{equation} 
  	\frac{\dot n \left(t\right)}{n\left(t\right) / t} < \theta_n,
  \end{equation} 
  where the threshold $\theta_n$ is chosen to be much less than one, and specifically
   in the analysis here it is chosen as $\theta_n = 1 / 16$. Increasing this parameter might stop integration prematurely, whereas decreasing it will worsen performance.
  An analytic expression similar to Eq.~(\ref{eq.axionLagrangian.II}), however,  cannot be derived  for  non-zero $\alpha_2$ and $\alpha_3$. In this case,  equations for the auxiliary fields $F_k$ are  solved numerically,  and the Lagrangian in terms of $\phi$ (Eq.~(\ref{Lag.23})) is
  also evaluated numerically for each set of values for ($a_-$, $\dot a_-$).  
   This process is significantly slower, therefore, in this case the simulations are only done for $29$ sets of parameter values as can be seen in Fig.~(\ref{fig3}). 
    The time of horizon exit is then found by counting $N_\text{pivot}$ e-foldings back from the end of integration, where $N_\text{pivot}$ is varied between $50$ and $60$. Note, the time of horizon exit depends on $\theta_n$, however, we find that due to $\dot n$ being small near the end of integration, the dependence is weak, and it affects the results less than the experimental uncertainty of $N_\text{pivot} \in \left[50, 60\right]$.{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion\label{sec7}}
	In this work we have analyzed inflation in a supersymmetric Dirac-Born-Infeld action with a $U(1)$ symmetry.
	Specifically we have carried out a detailed analysis of a pair of chiral DBI fields which possess opposite charges
	under the $U(1)$ symmetry. A transformation is then made to go to the co-ordinate frame where a linear
	combination of the axion fields is invariant under the global $U(1)$ transformations and an orthogonal combination
	is variant which acts as the inflaton. The $U(1)$ shift symmetry is broken by instanton type non-perturbative terms
	in the superpotential. The analysis is done
	in the vacuum state with stabilized saxions and the scalar potential can be decomposed into a fast-roll and a slow-roll
	part where the slow-roll part of the potential is now velocity dependent. This velocity dependence is a direct consequence of the
	DBI form of the action. In the analysis we have obtained an explicit form for the auxiliary fields $F_k$ which satisfy a cubic equation
	in terms of the inflation field. We have analyzed the scalar and tensor power spectrum and computed the spectral indices.
	It is shown that a significant part of the parameter space exists which supports inflation consistent with the current experimental
	constraints on the ratio of the tensor to the scalar power spectrum and the spectral indices. A remarkable aspect of the
	proposed supersymmetric DBI model is that the model supports an observable value of the tensor to the scalar power spectrum
	and consequently also a significant value for the spectral index $n_t$. This is in contrast to a supersymmetric non-DBI model
	which typically has a suppressed value of $r$ and of $n_t$. An analysis of non-Gaussianity in the model was also carried out.
	It is found that for the model parameters that support inflation consistent with the Planck experimental values on $r$ and
	$n_s$, the non-Gaussianity is typically small. It is of interest to achieve this class of models in string theory using
	moduli stabilization of the type used in KKLT~\cite{Kachru:2003aw}
	or the Large Volume Scenario~\cite{Balasubramanian:2005zx}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
	This research was supported in part by the NSF Grant PHY-1620575.

@@

	superfield. Thus we consider a supersymmetric DBI Lagrangian of the form

>>>>

\documentclass[12pt]{article}

% Math Related Packages
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{bbm}
%\usepackage{cancel}
%\usepackage{mathtools}
\usepackage{slashed}
\usepackage[numbers,sort&compress]{natbib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
%%%%
\usepackage{cleveref}
\crefname{equation}{Eq.}{Eqs.}
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
\crefname{section}{Section}{Sections}
\newcommand{\crefrangeconjunction}{--}
%%%

\def\non{\nonumber\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting Related Packages
\usepackage[letterpaper,margin=1in,bottom=1in]{geometry}
\usepackage{float} % allows forcing plot and table locations with [H]
\usepackage{parskip} % skip spaces between paragraphs
\usepackage{tabulary} % table environment with auto word wrapping
\usepackage{color} % color for tracking edits
\usepackage{soul} % strikeout for tracking edits
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage[section]{placeins} % keep figures inside their sections

\def\lhc2{LHC~Run~II}
\def\nsu{nonuniversal~supergravity~models~}
\def\dd{$\cdot\cdot$}

% Reference Package
\usepackage{cleveref}

% Macros
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\GeV}{~\textrm{GeV}}

%\bibliographystyle{suj_long}
\bibliographystyle{suj}

%%%%%%%%%
%% FLN
%\newcommand{\GeV}      {~\mathrm{GeV}}
\newcommand{\pb}      {~\mathrm{pb}}
\def\nj{$n_{jet}$}
\def\njs{$n_{jet}^*$}
\def\co{coannihilation~}
\def\pts{$P_T^{\rm * miss}$}
\def\pt{\not\!\!{P_T}}
\def\no{\nonumber\\}
\def \chan{\widetilde{\chi}}
\def \cha{\widetilde{\chi}^{\pm}_1}
\def \chb{\widetilde{\chi}^{\pm}_2}
\def \na{\widetilde{\chi}^{0}}
\def \nb{\widetilde{\chi}^{0}_2}
\def \nc{\widetilde{\chi}^{0}_3}
\def \nd{\widetilde{\chi}^{0}_4}
\def \g{\tilde{g}}
\def \ql{\widetilde{q}_L}
\def \qr{\widetilde{q}_R}
\def \dl{\widetilde{d}_L}
\def \dr{\widetilde{d}_R}
\def \ul{\widetilde{u}_L}
\def \ur{\widetilde{u}_R}
\def \ccl{\widetilde{c}_L}
\def \ccr{\widetilde{c}_R}
\def \ssl{\widetilde{s}_L}
\def \ssr{\widetilde{s}_R}
\def \ta{\widetilde{t}_1}
\def \tb{\widetilde{t}_2}
\def \ba{\widetilde{b}_1}
\def \bb{\widetilde{b}_2}
\def \sta{\widetilde{\tau}_1}
\def \stb{\widetilde{\tau}_2}
\def \smr{\widetilde{\mu}_R}
\def \ser{\widetilde{e}_R}
\def \sml{\widetilde{\mu}_L}
\def \sel{\widetilde{e}_L}
\def \slr{\widetilde{l}_R}
\def \sll{\widetilde{l}_L}
\def \snl{\widetilde{\nu}_{\tau}}
\def \snm{\widetilde{\nu}_{\mu}}
\def \sne{\widetilde{\nu}_{e}}
\def \hc{H^{\pm}}
\def \lra{\longrightarrow}
\def \ETmiss{${\not\!\!{E_T}}~$}
\def \missET{${\not\!\!{E_T}}$}
\def \mh{m_{1/2}}
\def\.4{\vspace{-.5cm}}
\newcommand{\ifb}{~\textrm{fb}^{-1}}
\newcommand{\iab}{~\textrm{ab}^{-1}}

\def\beq{\begin{equation}}
\def\be{\begin{equation}}
\def\beqn{\begin{eqnarray}}
\def\ee{\end{equation}}
\def\eeq{\end{equation}}
\def\eeqn{\end{eqnarray}}
\newcommand{\bl}[1]{{\color{blue}{#1}}}
\newcommand{\pn}[1]{{\color{red}{#1}}}
\newcommand{\gr}[1]{{\color{green}{#1}}}
\def\co{coannihilation~}
\def\TeV{\rm{TeV}}

\def\co{coannihilation~}
\def\G{\tilde G}
\def\mP{M_{\rm Pl}}

\author{
Pran Nath\footnote{Email: p.nath@northeastern.edu}~\ and 
Maksim Piskunov\footnote{Email:m.piskunov@northeastern.edu}\\~\\
Department of Physics, Northeastern University,
Boston, MA 02115-5000, USA
}

\title{Supersymmetric Dirac-Born-Infeld Axionic Inflation and Non-Gaussianity}

\begin{document}
\maketitle
\date

\textbf{Abstract: } 
  An analysis is given of inflation based on a supersymmetric Dirac-Born-Infeld (DBI) action in
  an axionic landscape. The DBI model we discuss involves a landscape of chiral superfields with one
  $U(1)$ shift symmetry which is broken by instanton type non-perturbative terms
  in the superpotential. Breaking of the shift symmetry leads to one pseudo-Nambu-Goldstone-boson which acts as
  the inflaton while the remaining normalized phases of the chiral fields
  generically labeled axions are invariant under the
  $U(1)$ shift symmetry. The analysis is carried out in the vacuum with stabilized saxions,
 which are the magnitudes of
  the chiral fields. Regions of the parameter space where slow-roll inflation occurs are exhibited and the spectral
  indices as well as the ratio of the tensor to the scalar power spectrum are computed. An interesting aspect of supersymmetric
  DBI models analyzed is that in most of the parameter space tensor to scalar ratio and scalar spectral index are consistent with
   Planck data if     slow roll occurs and is not eternal. Also interesting is that
  the ratio of the tensor to the scalar power spectrum can be large and can lie close to the
  experimental upper limit and thus testable in improved
  experiment. Non-Gaussianity in this
  class of models is explored.
\newpage

@@

    k=\tilde\beta \sqrt{\sum_{m, n}m n {\cal{G}}_m {\cal {G}}_n \left(1-\cos\left(\frac{a_- m}{\sqrt 2 f}\right)-\cos\left(\frac{a_- n}{\sqrt 2 f}\right)+\cos\left(\frac{a_- \left(m-n\right)}{\sqrt 2 f}\right)\right)},

@@

    {\cal{G}}_k = \frac{A_k 2^{1/2 (1 - k)}}{\tilde \beta \sqrt T f^{1-k}}\,.

@@

  Here $\tilde \beta$ is an arbitrary dimensionless parameter which we choose such that ${\cal{G}}_k \sim 1$, and which determines the scale of symmetry breaking terms relative to $T$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pressure, density and inflation equations \label{sec4}}
  The pressure $p$ and density $\rho$ are defined in terms of the stress tensor by
  \begin{equation}\label{DisplayFormulaNumbered:eq.pressure}
    p= \frac{1}{3} \sum_{i=1}^3 T^{ii}\,,
    ~~\rho =T^{00},
  \end{equation}
  where $T^{\mu\nu}$ $(\mu=0, 1, 2, 3)$ is the stress tensor and is given by
  \begin{equation}
    T^{\mu \nu}=g^{\mu \nu} \mathcal{L}\left(\phi_k,\partial_\mu \phi_k \partial^\mu \phi_k \right)-2\frac{\delta \mathcal{L}\left(\phi_k,\partial_\mu \phi_k \partial^\mu \phi_k \right)}{\delta \left(\partial_\mu \phi_k \partial^\mu \phi_k \right)}\partial^\mu \phi_k \partial^\nu \phi_k,
    \label{tmunu}
  \end{equation}
  and we use the metric $\eta^{\mu\nu}= {\rm diag}(-1, 1, 1, 1)$.
  In the analysis we assume space to be homogeneous and isotropic, so that $\partial_i\phi_k = 0$ for $1 \leq i \leq 3$ and 
	$\partial_0 \phi_{k} = \dot{\phi}_k$,
  one finds that Eqs. (\ref{DisplayFormulaNumbered:eq.pressure}) and (\ref{tmunu})
  for pressure and density become:
  \begin{equation}\label{DisplayFormulaNumbered:eq.pressure.cosmology}
    p = \mathcal{L}\left(\phi_k, - \beta_k \right),
  \end{equation}
  and
  \begin{equation}\label{DisplayFormulaNumbered:eq.density.cosmology}
    \rho = -\mathcal{L}\left(\phi_k, - \beta_k\right) + 2\sum_{k}\frac{\delta \mathcal{L}\left(\phi_k, - \beta_k \right)}{\delta \beta_k}
    \beta_k,
  \end{equation}
  where $\beta_k = \dot \phi_k^2$.
  These relations are valid for non-canonical kinetic terms.
  The Friedman equations are given by
  \begin{align}
    \dot \rho = -3H (p + \rho),
    \label{fried1}
  \end{align}
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = \rho,
    \label{fried2}
  \end{align}
  \begin{align}
    \dot\rho= - 6H \sum_{k} \frac{\partial L}{\partial \beta_k} \beta_k\,.
    \label{rhodot1}
  \end{align}
  Further taking the time derivative of Eq.~(\ref{DisplayFormulaNumbered:eq.density.cosmology})
  which along with Eq.~(\ref{rhodot1}) gives
  \begin{align}
    &\sum_{k}\Big[ \left(2 \frac{\partial^2 L}{\partial \beta_k \partial \beta_k} \beta_k + \frac{\partial L}{\partial \beta_k}
    \right)\dot \beta_k
    - \frac{\partial L}{\partial \phi_k} \dot \phi_k + 6H \frac{\partial L}{\partial \beta_k} \beta_k
    + 2 \frac{\partial^2 L}{\partial \phi_k\partial \beta_k} \beta\dot \phi_k \Big]=0.
    \label{motion}
  \end{align}
  Next we focus on the slow-roll part where we keep only the field $a_-$. In this case Eqs. (\ref{fried2}) and (\ref{motion}) can be written in
  the following form
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = 2 \dot a_{-}^2 \frac{\partial L}{\partial \dot a_{-}^2} - L\,,
    \label{inf-1a}
  \end{align}
  \begin{align}
    2 \left[2 \frac{\partial^2 L}{\partial \dot a_{-}^2 \partial \dot a_{-}^2} \dot a_{-}^2 + \frac{\partial L}{\partial \dot a_{-}^2}
    \right] \ddot a_{-} -
    \frac{\partial L}{\partial a_{-}} + 6H \dot a_{-} \frac{\partial L}{\partial \dot a_{-}^2}
    + 2 \frac{\partial^2 L}{\partial a_{-} \partial \dot a_{-}^2} \dot a_{-}^2
    =0
    \label{inf-2a}\,.
  \end{align}
  For the case of canonical kinetic energy and no dependence of the potential on time derivative of field, i.e.,
  \begin{align}
    L= -\frac{1}{2} \partial_\mu a_{-}\partial a_{-}^{\mu} - V(a_-)
  \end{align}
  Eqs. (\ref{inf-1a}) and  (\ref{inf-2a}) 
   reduce to the following
  \begin{align}
    3 M_\text{P}^2 \frac{\dot R^2}{R^2} = \frac{1}{2} \dot a_{-}^2 + V(a_-)\,,\non
    \ddot a_{-} + 3 H \dot a_{-} + V'(a_{-})=0\,,
  \end{align}
  which are correctly the relation for slow roll for the case when one has canonical kinetic energy and the potential
  is velocity independent. However, in our case we have more terms.

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{fig1.pdf}
    \caption{
      Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the scalar spectral index $n_s$ 
      for the two field DBI model when $\alpha_1$ is allowed to vary, when $\alpha_2 = \alpha_3 = 0$. 
      The blue region enclosed by the blue line is the one allowed by experiment in the 2$\sigma$ range.      
            All the scatter points have pivot number of e-foldings in the range [50, 60].          
         $89\%$ of the simulated points 
      are consistent with Planck constraints as shown by green points while the red points lie outside the 68\% CL contour.
            Right panel: A plot of non-Gaussianity parameter $f_{NL}$ as
      a function of $\alpha_1$ for the same data set as in the left plot.  As in the left panel
      the green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region  
      and the red dots are parameter points which are outside the experimentally allowed region  on $r$ and $n_s$. The horizontal black line is the
 lower limit $f_{NL} =5$ of the 
        projected value for observation in future experiments for non-Gaussianity.
           The points that lie above the black line give non-Gaussianity $f_\text{NL} > 5$ which, however, are not consistent with Eq.~(\ref{data}).
    }
    \label{fig1}
  \end{figure}

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{fig2.pdf}
    \caption{Left panel: A plot of the ratio $n_s$ vs $N_{\rm pivot}$ in the range $50-60$ for the same data set as in Fig.~(\ref{fig1}).
    The plot shows a mild dependence of $n_s$ on $N_{\rm pivot}$ in the range indicated. Right panel: The same as the left panel except
    $f_{NL}$ is plotted vs $N_{\rm pivot}$.
    The green and red dots are parameter points and have the same meaning as in Fig.~(\ref{fig1}).}
    \label{fig2}
  \end{figure}

  \begin{figure}
  	\centering
  	\includegraphics[width=1.0\textwidth]{fig3.pdf}
  	\caption{The effect of $\alpha_2$ (left panel) and $\alpha_3$ (right panel) on non-Gaussianity for a parameter point 
	taken from Fig.~(\ref{fig1}) which is consistent with 
	Planck data and has the  largest non-Gaussianity among the set of parameter points 
  in Fig.~(\ref{fig1}). Specifically, here $f = 0.429 M_\text{P}$, $a_{-, 0} = 0.233 M_\text{P}$, $\dot a_{-, 0} = -0.118 M_\text{P}^2$, ${\cal{G}}_1 = {\cal{G}}_2 = {\cal{G}}_3 = 0$, ${\cal{G}}_4 = 1$, ${\cal{G}}_5 = -1.53$, ${\cal{G}}_6 = 563$, $\alpha_1 = 1207$, $\tilde \beta = 0.802$, $T = M_\text{P}^4$. One 
	finds that 
	 the effect is not sufficient to obtain a significantly larger value of $f_\text{NL}$.}
  	\label{fig3}
  \end{figure}

Numerical simulations performed consist of two parts: a large $0.5 \times 10^6$ points simulation in which $\alpha_2 = \alpha_3 = 0$, and a small simulation with $\alpha_2$ and $\alpha_3$ perturbed around an experimentally consistent point with the largest non-Gaussianity from the first simulation.
  The evolution of the inflaton field $a_-$ in the large simulation of Figs.~(\ref{fig1}) and (\ref{fig2}) is obtained by taking the effective axion Lagrangian Eqs.~(\ref{eq.axionLagrangian.I}) and (\ref{eq.axionLagrangian.II}), deriving Euler-Lagrange equation and Friedmann Eq.~(\ref{fried2}) using computer algebra, and solving them numerically. The integration is stopped when the ratio of the time derivative ($\dot n\left(t\right)$) of the e-foldings count to its time-average ($n\left(t\right) / t$) passes a threshold. Specifically,
  \begin{equation} 
  	\frac{\dot n \left(t\right)}{n\left(t\right) / t} < \theta_n,
  \end{equation} 
  where the threshold $\theta_n$ is chosen to be much less than one, and specifically
   in the analysis here it is chosen as $\theta_n = 1 / 16$. Increasing this parameter might stop integration prematurely, whereas decreasing it will worsen performance.
  An analytic expression similar to Eq.~(\ref{eq.axionLagrangian.II}), however,  cannot be derived  for  non-zero $\alpha_2$ and $\alpha_3$. In this case,  equations for the auxiliary fields $F_k$ are  solved numerically,  and the Lagrangian in terms of $\phi$ (Eq.~(\ref{Lag.23})) is
  also evaluated numerically for each set of values for ($a_-$, $\dot a_-$).  
   This process is significantly slower, therefore, in this case the simulations are only done for $29$ sets of parameter values as can be seen in Fig.~(\ref{fig3}). 
    The time of horizon exit is then found by counting $N_\text{pivot}$ e-foldings back from the end of integration, where $N_\text{pivot}$ is varied between $50$ and $60$. Note, the time of horizon exit depends on $\theta_n$, however, we find that due to $\dot n$ being small near the end of integration, the dependence is weak, and it affects the results less than the experimental uncertainty of $N_\text{pivot} \in \left[50, 60\right]$.{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion\label{sec7}}
	In this work we have analyzed inflation in a supersymmetric Dirac-Born-Infeld action with a $U(1)$ symmetry.
	Specifically we have carried out a detailed analysis of a pair of chiral DBI fields which possess opposite charges
	under the $U(1)$ symmetry. A transformation is then made to go to the co-ordinate frame where a linear
	combination of the axion fields is invariant under the global $U(1)$ transformations and an orthogonal combination
	is variant which acts as the inflaton. The $U(1)$ shift symmetry is broken by instanton type non-perturbative terms
	in the superpotential. The analysis is done
	in the vacuum state with stabilized saxions and the scalar potential can be decomposed into a fast-roll and a slow-roll
	part where the slow-roll part of the potential is now velocity dependent. This velocity dependence is a direct consequence of the
	DBI form of the action. In the analysis for the case $\alpha_2=0=\alpha_3$
	 we have obtained an explicit form for the auxiliary fields $F_k$ which satisfy a cubic equation
	in terms of the inflation field. We have analyzed the scalar and tensor power spectrum and computed the spectral indices.
	It is shown that a significant part of the parameter space exists which supports inflation consistent with the current experimental
	constraints on the ratio of the tensor to the scalar power spectrum and the spectral indices. A remarkable aspect of the
	proposed supersymmetric DBI model is that the model supports an observable value of the tensor to the scalar power spectrum
	and consequently also a significant value for the spectral index $n_t$. This is in contrast to a supersymmetric non-DBI model
	which typically has a suppressed value of $r$ and of $n_t$. An analysis of non-Gaussianity in the model was also carried out.
	It is found that for the model parameters that support inflation consistent with the Planck experimental values on $r$ and
	$n_s$, the non-Gaussianity is typically small. This holds true even when the parameters $\alpha_2$ and $\alpha_3$ along with
	$\alpha_1$ are included in the analysis.
		It is of interest to achieve this class of models in string theory using
	moduli stabilization of the type used in KKLT~\cite{Kachru:2003aw}
	or the Large Volume Scenario~\cite{Balasubramanian:2005zx}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Acknowledgments:}
	This research was supported in part by the NSF Grant PHY-1620575.

@@

	superfield. Thus we consider a supersymmetric DBI Lagrangian of the form~\cite{Rocek:1997hi,Tseytlin:1999dj,Sasaki:2012ka}	
